CLT item selection

### 2022-04-21 analysis/clt_item_selection.Rmd
Initial implementation of subset selection via simulated annealing.

ggplot(comp2, aes(x = mean_full, y = mean_sub))+
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = .75)+
  geom_jitter(pch = 1, alpha = .75, height = 0.01, width = 0.01)+
  stat_cor()+
  facet_wrap(~age_group)+
  ylim(0,1.02)+
  xlim(0,1.02)+
  theme_few()

>>>>

ggplot(comp2, aes(x = mean_full, y = mean_sub))+
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = .75)+
  geom_jitter(pch = 1, alpha = .75, height = 0.01, width = 0.01)+
  stat_cor()+
  facet_wrap(~age_group)+
  ylim(0,1.02)+
  xlim(0,1.02)+
  theme_few()
```

# Optimum subset selection via simulated annealing

```{r}

score_fn <- function(subset) {
	easinesses <- sort(easiness[subset])
	nn_dists <- rep(0, sum(subset)-1)
	for(i in 1:sum(subset)-1) {
		nn_dists[i] <- easinesses[i+1] - easinesses[i]
	}
	spacing <- -1*sd(nn_dists)
	mean_discrim <- mean(discrimination[subset])
	return(spacing + mean_discrim / 6)
}

proposal_fn <- function(subset) {
	swaps <- sample(c(1, 1, 1, 2, 2, 3), 1)
	for(i in 1:swaps) {
		active_items <- seq(1:length(subset))[subset == TRUE]
		inactive_items <- seq(1:length(subset))[subset == FALSE]
		active_to_swap <- sample(active_items, 1)
		inactive_to_swap <- sample(inactive_items, 1)
		subset[active_to_swap] <- FALSE
		subset[inactive_to_swap] <- TRUE
	}
	return(subset)
}

simulated_annealing <- function(k) {
	easiness <- filter(model_params, nlpar=="Easiness") %>% pull(Estimate)
	discrimination <- filter(model_params, nlpar=="Discrimination") %>% pull(Estimate)
	N <- length(easiness)

	best_subset <- sample(c(rep(TRUE, k), rep(FALSE, N-k)))
	best_score <- score_fn(best_subset)

	temp <- 100
	rejected <- 0
	for(i in 1:1e6) {
		new_subset <- proposal_fn(best_subset)
		new_score <- score_fn(new_subset)
		accept_decrease <- rbernoulli(1, temp / 100)
		if(new_score > best_score | accept_decrease) {
			best_subset <- new_subset
			best_score <- new_score
			print(best_score)
		} else {
			rejected <- rejected + 1
		}
		if(rejected == 100000) {
			break
		}
		temp <- temp*0.999
	}
	return(best_subset)
}
```
